GLM Predictor Matrices

### 2020-12-16 workflow/scripts/predictor_matrices.Rmd
analyze traj rmd

@@

Map of Europe and part of Asia showing the demes included in the analysis (in color). The X represents the centroid of each deme. The centroids of each European country fromm the Other European deme are not drawed.

<!-- Other distance ptions: -->
<!-- Average pairwaise distance between airports - considers that only flight transportation matters, more work -->
<!-- Distance taking into account population distribution inside the country. CEPPI dataset -->
<!-- Minimum distance. -->

>>>>

Analysis Europe 6 without indicator variables, Europe 7 with indicator variables, same predictors.

@@

Map of Europe and part of Asia showing the demes included in the analysis (in color). The X represents the centroid of each deme. The centroids of each European country from Other European deme are not drawed.

<!-- Other distance options: -->
<!-- Average pairwaise distance between airports - considers that only flight transportation matters, more work -->
<!-- Distance taking into account population distribution inside the country. CEPPI dataset -->
<!-- Minimum distance. -->
